---
title: "Causal Effect"
author: "Ronit Dash"
format: html
execute: 
  echo: false
---

```{r}
#| message: FALSE
library(tidyverse)
library(primer.data)
library(brms)
library(tidybayes)
library(gtsummary)
```

```{r}
ch6 <- trains |>  select(att_end, treatment)
ndata <- tibble(treatment = c("Treated", "Control"))
```

We are attempting to find the attitudes of people towards immigration when being exposed to Spanish-speakers using a 2012 study on Boston commuters. The time spread between the data and contemporary times may cause the relationships between opinions different, which is a potential problem. We modeled a graph to summarize the attitudes on immigration. The average causal effect was mostly in the 95% confidence interval of 1.5-2.5, and hearing Spanish-Speakers caused more conservative shifting.

```{r}
#| cache: TRUE
fit_gauss <- brm(formula = att_end ~ treatment,
  data = ch6, 
  family = gaussian(), 
  refresh = 0, silent = 2, seed = 9)
```

```{r}
tbl_regression(fit_gauss)
```
The posterior, or the coefficient of Control is centered around −1.5 with a 95% Confidence Interval between −2.5 and −0.5.

```{r}
fit_gauss |> add_epred_draws(newdata = ndata) |>
select(treatment, .draw, .epred) |> 
pivot_wider(id_cols = .draw, names_from = treatment, values_from = .epred) |>
mutate(causal_effect = Treated - Control) |>
select(- .draw) |> ggplot(aes(x = causal_effect)) +
geom_histogram(aes(y = after_stat(count / sum(count))), bins = 100) +
scale_y_continuous(labels = scales::percent_format()) + theme_classic() +
labs(title = "Posterior for Average Treatment Effect",
subtitle = "Exposure to Spanish-speakers shifts immigration attitudes rightward", 
x = "Difference in Attitude", y = "Probability")
```

